Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-08-01 paper/paper.tex
refactoring to restablish coherence

The overarching goal of our study is to identify the ability of
cross-engine differential testing to find bugs in \js\ engines.  We
analyzed the impact of two orthogonal dimensions in this study: test
mining and fuzzing. The first dimension focuses on the impact of
inputs, mined from the web, in bug finding whereas the second
dimension focuses on the impact of fuzzing those inputs.

In the following, we describe the methodology we used in this
experiment. Recall that our tool outputs a set of buckets, that each
bucket includes a set of warnings, that each warning is related to one
file, and that a bucket is of ``lo'' or ``hi'' importance, according
to the heuristic we defined. Figure~\ref{fig:distribution} shows the
distribution of number of warnings per bucket. We use the the label
``nofuzz'' to refer to the experiment that analyzed the impact of test
mining as we do not use fuzzing in that experiment and use the names
of the fuzzing tools to refer to the results obtained with those
tools. We inspected each and every bucket for bugs, but observe that
the number of files per bucket is very high in some cases (\eg{},
nofuzz [hi]). As such, it would be impractical to manually inspect all
the files in the bucket. For that reason, we only inspected one file
per bucket. For the cases we found the warning suspicious, we analyzed
the parts of the documentation related to the problem and, if still
suspicious, we looked on the bug tracker of the affected engine for
potential duplicates. If none was reported, we filed a bug report
including the test input that manifested the potential problem and
explaining the reasons we were suspicious. In some cases, we used the
Mozila lithium tool~\cite{lithium} to minimize the test case. For the
cases of false positives, we identified the source of false positive
and moved to the next bucket. Table~\ref{tab:summary-of-results}
summarizes our results. It shows, for each execution mode and category
of bucket (\ie{}, hi or lo), the total number of files involved, the
number of buckets reported by our infrastructure, the number of those
that we classified as bug-revealing, and the number of those that we
filed a bug report. The difference between the last two columns
indicate the number of duplicates, \ie{}, the cases of
already-reported bugs. As expected, the hit ratio for the ``hi'' group
is higher.

\begin{table}[t]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
    \cline{4-6}    
    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
    \multicolumn{1}{c}{\# pos. filed} \\
    \midrule
    \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crrr}
    \toprule
              & nofuzz & \radamsa\ & \quickfuzz\ \\
%    duplicate & 63      & - & - \\
    not yet implemented & 8 & - & - \\
    invalid input & 0 & - & - \\
    timeout/ome & 13 & - & - \\
    implementation-dependent & 3 & - & - \\
    future feature & 3 & - & - \\
    \bottomrule     
  \end{tabular}
\end{table}

\subsection{No Fuzzing}

This section reports the results obtained without fuzzing. The goal is
to observe the impact of the mined test cases in revealing
differential bugs. In this experiment, we ran all tests (see
Section~\ref{sec:seeds}) using our infrastructure in no-fuzzing
mode.

>>>>

The overarching goal of our study is to identify the ability of
cross-engine differential testing to find bugs in \js\ engines. We
organized our study in two parts. First, we investigated the stability
of the engines we analyzed. The intuition is that discovered bugs
would have low relevance if the engines are unstable. Then, we
analyzed the impact of using cross-engine differential testing to find
bugs in \js{} engines.

\subsection{Stability of Engines}

We evaluated stability using different source of test cases. We used
the official \js{} conformance test suite and test suites developed
independently by each engine developing team. The Test262 suite is the
primary suite that we used to assess stability of engines. We ran this
suite once per day for seven consecutive days. Table~\ref{tab:test262}
shows results. To sum, we observed that \Fix{...}

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Results of Test262.}
  \begin{tabular}{crrrrrrr}
    \toprule
           & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \jsc{} & - & - & - & - & - & - & - \\
    \veight{} & - & - & - & - & - & - & - \\
    \chakra{} & - & - & - & - & - & - & - \\
    \smonkey{} & - & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

We expanded these results by looking for tests from different
sources. \Fix{elaborate} Table~\ref{tab:cross-testing} shows
results. To sum, we observed that \Fix{...}

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Crossed execution of test suites..}
  \begin{tabular}{crrrr}
    \toprule
    test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
    Mozilla & - & - & - & -  \\
    v8 & - & - & - & -  \\
    WebKit & - & - & - & -  \\
    Duktape & - & - & - & -  \\
    JerryScript & - & - & - & -  \\
    JSI & - & - & - & -  \\
    Tiny-js & - & - & - & -  \\
    \bottomrule 
  \end{tabular}
\end{table}

%% Our infrastructure reported a total of \nofuzzAll{} buckets, including
%% \lo{} and \hi{}, that resulted in \nofuzzBugs{} bug reports. Of the
%% total of \nofuzzAll{} buckets, we found that \nofuzzDuplicates\ were
%% duplicates and \nofuzzFalsePositives\ were false positives. Most of
%% the cases of duplicates were related to the Test262 conformance test
%% suite, which all \js{} should strive to pass but we found that it is
%% not uncommon for the engines to fail on some of these. For example,
%% \veight{} \nofuzzFalsePositives

\subsection{Differential Testing}

In the following, we describe the methodology we used to asses the
impact of cross-engine differential testing in finding bugs on \js{}
engines. Recall that our tool outputs a set of buckets, that each
bucket includes a set of warnings, that each warning is related to one
file, and that a bucket is of ``lo'' or ``hi'' importance, according
to the heuristic we defined. Figure~\ref{fig:distribution} shows the
distribution of number of warnings per bucket. We use the the label
``nofuzz'' to refer to the experiment that analyzed the impact of test
mining as we do not use fuzzing in that experiment and use the names
of the fuzzing tools to refer to the results obtained with those
tools. We inspected each and every bucket for bugs, but observe that
the number of files per bucket is very high in some cases (\eg{},
nofuzz [hi]). As such, it would be impractical to manually inspect all
the files in the bucket. For that reason, we only inspected one file
per bucket. For the cases we found the warning suspicious, we analyzed
the parts of the documentation related to the problem and, if still
suspicious, we looked on the bug tracker of the affected engine for
potential duplicates. If none was reported, we filed a bug report
including the test input that manifested the potential problem and
explaining the reasons we were suspicious. In some cases, we used the
Mozila lithium tool~\cite{lithium} to minimize the test case. For the
cases of false positives, we identified the source of false positive
and moved to the next bucket. Table~\ref{tab:summary-of-results}
summarizes our results. It shows, for each execution mode and category
of bucket (\ie{}, hi or lo), the total number of files involved, the
number of buckets reported by our infrastructure, the number of those
that we classified as bug-revealing, and the number of those that we
filed a bug report. The difference between the last two columns
indicate the number of duplicates, \ie{}, the cases of
already-reported bugs. As expected, the hit ratio for the ``hi'' group
is higher.

\begin{table}[t]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
    \cline{4-6}    
    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
    \multicolumn{1}{c}{\# pos. filed} \\
    \midrule
    %% \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
    %% & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    %% not yet implemented & 8 & - & - \\
    %% invalid input & 0 & - & - \\
    %% timeout/ome & 13 & - & - \\
    %% implementation-dependent & 3 & - & - \\
    %% future feature & 3 & - & - \\
    not yet implemented & - & - \\
    invalid input & - & - \\
    timeout/ome & - & - \\
    implementation-dependent & - & - \\
    future feature & - & - \\
    \bottomrule     
  \end{tabular}
\end{table}
